\documentclass[11pt,largemargins, letter]{homework}

\newcommand{\hwname}{Tobias Jakobi}
\newcommand{\hwemail}{tjakobi@arizona.edu}
\newcommand{\hwtype}{Project}
\newcommand{\hwnum}{2}
\newcommand{\hwclass}{CTS505}
\newcommand{\hwlecture}{2023}
\newcommand{\hwsection}{-11}

\usepackage[margin=1in]{geometry}
\usepackage{fontawesome5}


\renewcommand{\questiontype}{Task}

\begin{document}
\maketitle

The solutions for the tasks below should be saved in a single \texttt{.R} file, with comment lines highlighting each task, e.g.,

\begin{verbatim}
# this is the code for Task 1 a)
head(varX)
\end{verbatim}

Please include loaded libraries, loading of files, and all other commands in the file.

\question

\begin{itemize}

    \item Download the list of gene counts stored in the following file \\\texttt{https://links.jakobilab.org/p2\_counts}
    \item Identify the organism used for the experiment based on the provided gene IDs for the next tasks.
\end{itemize}

  \begin{alphaparts}

    \questionpart Establish a reasonable grouping of the provided samples based on the sample names.
    \questionpart Read the provided input file into \faRProject \hspace{0.1mm} with an appropriate function.
    \questionpart Use the \texttt{biomaRt} package or any other suitable ID conversion package to retrieve gene names for gene IDs.
  \end{alphaparts}

\question

  \begin{alphaparts}
    \questionpart Develop a suitable design formula as discussed in the class to perform differential gene expression analysis between your chosen groups.
    \questionpart Use the \texttt{edgeR} workflow to build an \texttt{DGElist} object.
    \questionpart Using \texttt{edgeR}, perform filtering and normalization of the imported count data.
    \questionpart Lastly, perform differential gene expression analysis and note the number of up- and down regulated genes.
  \end{alphaparts}

\question

  \begin{alphaparts}
    \questionpart Save a result table with differentially expressed genes filtered by p-value and FDR (0.05) and sorted by logFC.
  \end{alphaparts}



Please send your \faRProject \hspace{0.1mm} script and result file attachment via email to \texttt{tjakobi@arizona.edu}.

In case of questions, please do not hesitate to contact me.

\end{document}